Taking Dyads Seriously

### 2022-08-03 paper/6_appendix.tex
cleanup

\input{reiter_stam_coeftable}
\FloatBarrier

@@

\input{weeks_coeftable}
\FloatBarrier

@@

\input{gibler_coeftable}
\FloatBarrier

@@

\begin{figure}[ht]
	\centering
	\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
	\label{fig:ameBias_asa}
	\includegraphics[width=1\textwidth]{graphics/ameSimBias_all_asaProbit.pdf} \\
\end{figure}

\begin{figure}[ht]
	\centering
	\caption{Proportion of times the true value fell within the estimated 95\% confidence interval for the standard, AME, and oracle models from 1,000 simulations.}
	\label{fig:ameCalib_asa}
	\includegraphics[width=1\textwidth]{graphics/ameSimCover_all_asaProbit.pdf} \\
\end{figure}

@@

\begin{figure}[ht]
\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points. $X$ and $W$ are correlated at 0.4 in this case.}
\label{fig:ameBias_corrMed}
\includegraphics[width=1\textwidth]{graphics/ameSimBias_all_corrProbitMed.pdf} \\
\end{figure}

\begin{figure}[ht]
\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points. $X$ and $W$ are correlated at 0.7 in this case.}
\label{fig:ameBias_corrHi}
\includegraphics[width=1\textwidth]{graphics/ameSimBias_all_corrProbitHi.pdf} \\
\end{figure}

>>>>

\input{graphics/appendix_tableB1}
\FloatBarrier

@@

\input{graphics/appendix_tableB2}
\FloatBarrier

@@

\input{graphics/appendix_tableB3}
\FloatBarrier

@@

\begin{figure}[ht]
	\centering
	\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points.}
	\label{fig:ameBias_asa}
	\includegraphics[width=1\textwidth]{graphics/appendix_figureC1.pdf} \\
\end{figure}

\begin{figure}[ht]
	\centering
	\caption{Proportion of times the true value fell within the estimated 95\% confidence interval for the standard, AME, and oracle models from 1,000 simulations.}
	\label{fig:ameCalib_asa}
	\includegraphics[width=1\textwidth]{graphics/appendix_figureC2.pdf} \\
\end{figure}

@@

\begin{figure}[ht]
\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points. $X$ and $W$ are correlated at 0.4 in this case.}
\label{fig:ameBias_corrMed}
\includegraphics[width=1\textwidth]{graphics/appendix_figureD1a.pdf} \\
\end{figure}

\begin{figure}[ht]
\caption{Regression parameter estimates for the standard, AME, and oracle models from 1,000 simulations. Summary statistics are presented through a traditional box plot, and the estimates from each simulation are visualized as well as points. $X$ and $W$ are correlated at 0.7 in this case.}
\label{fig:ameBias_corrHi}
\includegraphics[width=1\textwidth]{graphics/appendix_figureD1b.pdf} \\
\end{figure}
